---
title: "Developing Data Products - Project 1"
author: "Jieqian Liu"
date: "Aug 9 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(leaflet)
```

## Introduction

Below is an interactive map created in Leaflet, as per the Coursera, Developing Data Products Week 2 project. I have chosen to use R's "quakes" dataset, which provides locations of seismic events in Fiji. <br />
The circle radii and color are scaled accoring to quake magnitude. The magnitude can be seen by clicking on a particular quake. <br />
Please note that as the instructions for the assignment ask for no more than 1) a map, and 2) a date, nothing more than that has been included.


```{r, echo=F}
data("quakes")
quakes_new <- quakes
```

## Map Code
```{r, echo=F}
exponent <- 6
# Make the magnitude differences more pronounced
quakes_new$mag <- quakes_new$mag^exponent
# Create a continuous palette function
pal <- colorNumeric(
  palette = "YlOrRd",
  domain = quakes_new$mag)
```

```{r, echo=F}
map <- leaflet(quakes_new) %>%
  addTiles() %>%
  addCircles(lat=~lat,
             lng=~long,
             color=~pal(mag),
             radius=~mag,
             weight=~depth%>%log(),
             popup=~mag%>%'^'(1/exponent)%>%paste("Magnitude:", .)
  )
map
```
